\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2011-02-07 article.tex
Added description to techniques by height

\SubSection{Techniques by Groups}

  In terms of category distribution, there are more blocks with the left side
  than there are with the right side. There are, therefore, more attacks with
  the right side, than with the left side (Table \ref{tab:table2}, Figure
  \ref{fig:techniques_all}).

@@

  Techniques by height follow the same pattern when looking at all techniques,
  as well as both sides. Most of the techniques are in the middle section,
  except for strikes which there are more of in the high section. There are
  very few punches, strikes and thrusts to the low section. In general, there
  are more blocks than any other technique.

>>>>

\SubSection{Techniques by Category}

  In terms of category distribution, there are more blocks on the left side
  than there are on the right side. There are, therefore, more attacks on the
  right side, than on the left side (Figure \ref{fig:techniques_all}, Table
  \ref{tab:table2}).

  Independent on side or total, all technique categories follow the same
  pattern having most blocks, then punches, strikes and finally thrusts.

@@

  Techniques by height follow the same trend when looking at all techniques
  combined or techniques to either side. In general, there are more blocks
  than any other technique. Most of the techniques are in the middle section,
  although there is a greater occurrence of strikes in the high section, and
  very few attacks in the low section.
